A Survey of Exoskeleton Control Architectures and Algorithms\\ (Draft 3.0)

### 2015-09-29 survey.tex
refs correected
about to pull
fixed bibliography

\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
% \usepackage{cite}
\usepackage{graphicx}
% \usepackage[dvips]{graphicx}
% \usepackage{epsfig} % for postscript graphics files
  % \graphicspath{{../eps/}}
% \DeclareGraphicsExtensions{.eps}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage[cmex10]{amsmath}
%\usepackage{array}
%\usepackage{mdwmath}
%\usepackage{mdwtab}
%\usepackage{eqparbox}
\usepackage[tight,footnotesize]{subfigure}
%\usepackage[caption=false]{caption}
%\usepackage[font=footnotesize]{subfig}
%\usepackage{fixltx2e}
%\usepackage{stfloats}
\usepackage{hyperref}
\usepackage[backend=biber]{biblatex}
\addbibresource{exos/bleex.bib}
\addbibresource{exos/hal.bib}
\addbibresource{exos/xor.bib}

@@

\begin{abstract}
In the simplest case, where the environment around a robotic system remains relatively fixed, controlling the dynamic interaction between the robot and the environment to achieve a specific physical objective is difficult.  In the case where an operator effectively wears the robot, i.e., a robotic exoskeleton, and would like to move through unknown and dynamically evolving environments, the situation becomes very complicated; the robotic system needs to account for for the dynamics of multiple fundamentally linked systems and that are for the most part difficult to model.  The goal of this document is to provide a survey of the literature on the design, modeling, and control of robotic exoskeletons and to highlight what we believe are several of the most promising currently existing approaches to the complicated goal of enabling dynamic yet safe interaction between operators, exoskeletons, and the environment.  Where information was available, we summarize specific contributions related to actuation, power storage and generation, sensor type and distribution, mechanical architecture, as well as control system design for a number of different exoskeleton hardware systems.  Included as part of this report are recommendations on what we see as helpful components as well as potentially problematic issues in current systems and control approaches. 
\end{abstract}

@@

>>>>

\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
% \usepackage{cite}
\usepackage{graphicx}
% \usepackage[dvips]{graphicx}
% \usepackage{epsfig} % for postscript graphics files
  % \graphicspath{{../eps/}}
% \DeclareGraphicsExtensions{.eps}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage[cmex10]{amsmath}
%\usepackage{array}
%\usepackage{mdwmath}
%\usepackage{mdwtab}
%\usepackage{eqparbox}
\usepackage[tight,footnotesize]{subfigure}
%\usepackage[caption=false]{caption}
%\usepackage[font=footnotesize]{subfig}
%\usepackage{fixltx2e}
%\usepackage{stfloats}
\usepackage{hyperref}
\usepackage[backend=biber]{biblatex}
\addbibresource{exos/bleex.bib}
\addbibresource{exos/hal.bib}
\addbibresource{exos/xor.bib}
\addbibresource{exos/bodyExt.bib}
\addbibresource{exos/dualMod.bib}
\addbibresource{exos/ihmc.bib}
\addbibresource{exos/mit.bib}
\addbibresource{exos/roboKnee.bib}

@@

\begin{abstract}
In the simplest case, where the environment around a robotic system remains relatively fixed, controlling the dynamic interaction between the robot and the environment to achieve a specific physical objective is difficult.  In the case where an operator effectively wears the robot, i.e., a robotic exoskeleton, and would like to move through unknown and dynamically evolving environments, the situation becomes very complicated; the robotic system needs to account for the dynamics of multiple fundamentally linked systems and that are for the most part difficult to model.  The goal of this document is to provide a survey of the literature on the design, modeling, and control of robotic exoskeletons and to highlight what we believe are several of the most promising currently existing approaches to the complicated goal of enabling dynamic yet safe interaction between operators, exoskeletons, and the environment.  Where information was available, we summarize specific contributions related to actuation, power storage and generation, sensor type and distribution, mechanical architecture, as well as control system design for a number of different exoskeleton hardware systems.  Included as part of this report are recommendations on what we see as helpful components as well as potentially problematic issues in current systems and control approaches. 
\end{abstract}

@@

Add references for new sensing tech
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
